Attacks on Neural Networks in a Lightweight Speech Anonymization Pipeline

### 2024-05-26 paper/paper.tex
Collected sources

@@

\section{Related Work}
\citet{meyer2023anonymizing}

\section{Method}

>>>>

\usepackage{natbib}

@@

\section{Related Work}
\citet{meyer2023anonymizing} % Work on neural speaker anonymization

\citet{shihao2024adversarial} % Work on attacking neural speaker anonymization

\citet{xiaoyong2019adversarial} % Often cited paper about adversarial examples and attacks, use for introducing the idea of attacks on neural networks

\citet{goodfellow2015explaining} % The paper about FGSM, use as intro to evasion attacks

\citet{madry2018towards} % The paper about PGD, which we will use, builds upon FGSM

\citet{gu2019badnets} % The paper about BadNets. Keep it brief. Use it to visualize the backdooring process.

\citet{liu2018trojaning} % The paper about trojanning audio. Keep it brief. Use it to show that backdooring audio is also possible.

\citet{stefanos2022ultrasonic} % The paper about ultrasonic frequencies for backdooring. Keep it brief. Another example of audio backdoor.

\citet{stefanos2023jingleback} % Jingleback paper. Explain in more details since you will focus on it.

\section{Method}
\citet{kai2022lightweight} % Work on lightweight speaker anonymization, idea for our method/pipeline.
